Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-21 Background.tex
Stigma, notation
More commentary in methods

This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \ac{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. \citet{Spence1973} demonstrated similar results in a game of job market signalling, where signal cost was differentiated by type. Costly signalling has also been suggested as an explaination of behaviour that at first gasp appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal carries a risk of being eaten. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications if ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.

Other work augments the signalling game model, for example \citet{Austen-Smith2005} adds a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subseqent empirical support for the idea from \citet{Jr2010}. On a similar tack, \citet{Feltovich2002} introduced additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality faail to do so.

@@

\begin{comment}Under this model, the expected utility of any gamble is a function
of the probability of the outcomes, their utility to the gambler,
and the gambler's risk aversion. Essentially this is an extension
of the expected value criterion, which assumes that the expected value
is based only on the probability and objective value of outcomes.
By contrast, the utility framing is a subjective measure, allowing
differing preferences between gamblers. \citet{Neumann1953} later
formalised the theory, defining rational decision as acting to maximise
expected utility, where an individual's preferences are shown to fulfil
four axioms, namely completeness, transitivity, independence, and
continuity. Completeness requires that for any two lotteries A and
B, the decision maker prefers one to the other, or is indifferent.
Transitivity requires that if A is preferred to B, and B is preferred
to C, then A is also preferred to C. Continuity states that given
a scenario as in the transitivity axiom, there is some combination
of lotteries A and C where the decision maker is indifferent between
that combined lottery and B. Finally, independence maintains that
if one were to prefer gamble A to B, that preference holds if both
are combined with lottery C.

Bayesian decision theory, as expounded by \citet{Robbins1964} applies
Bayesian inference to the process of decision making under some degree
of uncertainty, where decisions may be one-shot, or repeated.
The central idea is relatively straightforward, and assumes that the
loss or gain of some action to resolve a decision is contingent on
an unknown parameter. To solve the problem, the decision maker chooses
whichever action will minimise the risk, where the risk of an action
is $\underset{i}{\sum}\lambda(a_{j}|w_{i})P(w_{i}|x)$, i.e. the loss
incurred for taking action $a_{j}$ given that the true state of the
world is $w_{i}$, multiplied by the belief that this is the true
state of world given evidence $x$, summed across all possible worlds.
Essentially this is identical with expected value, with Bayesian style
probabilities. This allows an additional process of inference to progressively
update the distribution from which $P(w_{i}|x)$ derives, as new evidence
is obtained after each decision.

This approach has been used in a wide variety of scenarios, for example
\citet{McNamara1980} have applied statistical decision theory as
a framework for understanding animal learning%
\footnote{Although they note that this is in the sense of how animals `should'
learn, rather than how they do learn%
}, while \citet{Harsanyi1978} has derived an ethical framework from
the principles. Less controversially, in contexts where optimality
is desirable as an outcome, \citet{Survey2003} have used Bayesian
decision methods in combination with \ac{MCMC} to solve complex waterfowl
habitat management problems, and \citet{Kristensen1997} has developed
robots which utilise Bayesian decision analysis to plan sensor operations.

As with standard expected utility, the Bayesian approach can be criticised,
in this case on the grounds of plausibility. The question of plausibility
arises from the suggestion that Bayesian inference is in some way
a model of human inductive reasoning, as argued by some branches of
cognitive science. For example, \citeauthor{Tenenbaum2006} argue
for the Bayesian approach as a top-down model of inductive reasoning
in humans \citep{Tenenbaum2006,Griffiths2010}, a general approach
criticised by \citet{Bowers2012} as unfalsifiable, overcomplicated,
and relying on an unrealistic conceptualisation of the brain as optimal.
\citet{Miller2012} also applied similar criticism to claims by \citet{Gallistel2012}
that Bayesian inference better characterises learning as opposed to
associative conditioning type models, suggesting that this relies
on an assumption of optimality which is unfounded.

\subsubsection{Descriptive Decision Theory}

Arguably the most significant criticism of theories of decision making,
is their failure to correspond to empirically observed decision making
\footnote{This critique is not unique to decision theory, and has also been
levelled at game theory (e.g. \citet{Fehr2003} on the irrational
altruism of humans playing the prisoners' dilemma).%
}. This was probably first raised by \citet{Simon1956}, who proposed that the
apparent divergence derived from a tendency to satisfice, rather than
optimise. This suggestion rests on the not unreasonable assumption
that people do not have unlimited cognitive capacity (i.e. bounded
rationality \citep{Simon2000}), and hence use heuristic means to
make decisions, namely by choosing the first `good enough' option.
\citeauthor{Simon1956} suggests that this process nevertheless leads
to the optimal solution is most cases.

Subsequent work on descriptive theories largely follows the same framework
in assuming that in reality, human decision making is a heuristic
process. \citet{Tversky1974} developed three heuristics to explain
observed systematic errors in reasoning - representativeness, availability,
and anchoring. Representativeness suggests that when asked to judge
how related one object or event is to another, they do this based
on the extent to which they resemble one another - crucially they
will ignore additional, better information when available. Availability
claims that when tasked with estimating probabilities, people will
rely on the ease with which they can call examples to mind (note that
this might be considered an example of satisficing). Finally, anchoring
proposes that when estimating, people start with some initial value
and progressively update from there, i.e. they will tend to overweight
prior evidence at the expense of new information.

Subsequently, \citet{Kahneman1984,Tversky1986} also identified framing
effects, which imply that the decisions people make are impacted by
the fashion in which the problem is presented. The essential outcome
from these findings is that people are risk seeking when faced with
outcomes framed as losses, but risk averse towards gains, and regard
any loss as greater than an equivalent gain. The impact of framing
in itself has been shown to be significant, for example \citet{Toll2007}
found improved abstinence rates in smoking cessation where quitting
was framed as a gain, and \ac{NICE} recommend considering the framing
of treatment outcomes when presenting options to patients \citep{NICE2007}.

\ac{PT} \citep{Kahneman1979} attempts to provide a decision rule
accounting for the heuristic nature of decision making and incorporate
framing effects, which successfully explains many perceived failures
of rationality. A revised version, \ac{CPT} \citep{Tversky1992}
addressing a violation of first order stochastic dominance possible
under the original formulation, extends the theory to allow decisions
with more than two options, but sacrifices the editing phase. \citet{Camerer2004a}
reviews a number of successes in explaining apparent anomalies with
\ac{CPT}, and argues that should replace expected utility in general
usage. \citet{Thaler2000} regards the theory as promising, but points
out that it is in many ways incomplete, citing the lack of explanation
as to how people construct frames as an example of this.

A significant weakness of \ac{CPT} as a general theory of decision
making is that it fails to account for behaviour under intertemporal
choice, or rather does not attempt to address it. Generally, intertemporal
choice is assumed to be underpinned by the \ac{DU} model of \citet{Samuelson1937},
which proposes that the value of a thing right now is greater than
the value of it at some point in the future (jam today has more utility
than jam tomorrow), following an exponential relationship. A more
nuanced view of this has been proposed by \citet{Ainslie1991}, suggesting
that the relationship is hyperbolic rather than exponential. Both
models however fail to explain several inconsistencies, for example
\citet{Thaler1981} found that discounting rates were different between
gains and losses. \citet{Loewenstein1992} report a number of additional
inconsistencies that are not adequately resolved by \ac{DU} models,
and propose an alternative along the lines of \ac{CPT} to resolve
them while retaining the capabilities of Kahneman and Tversky's model
in immediate term choices.
\end{comment}

>>>>

This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \ac{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}. 
Costly signalling has also been suggested as an explaination of behaviour that at first gasp appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal carries a risk of being eaten. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications if ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.

Other work augments the signalling game model, for example \citet{Austen-Smith2005} adds a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subseqent empirical support for the idea from \citet{Jr2010}. On a similar tack, \citet{Feltovich2002} introduced additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality fail to do so.

@@

### 2014-07-21 Introduction.tex
More commentary in methods

Turning more specifically to disclosure of alcohol use during pregnance, research is relatively sparce, although qualitative trends are reported by \citet{Phillips2007}, and \citet{Alvik2006}. The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking. The simulation model described in this paper is able to replicate both qualitative trends, i.e. an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.

@@

two fold appeal. cognitive plausibility - neuroec. inaccessible systems (litigation, concealment). fast. cheap. portable. theoretical grounding. rigor.

>>>>

Turning more specifically to disclosure of alcohol use during pregnancy, research is relatively sparce, although qualitative trends are reported by \citet{Phillips2007}, and \citet{Alvik2006}. The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking. The simulation model described in this paper is able to replicate both qualitative trends, i.e. an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.

@@

%two fold appeal. cognitive plausibility - neuroec. inaccessible systems (litigation, concealment). fast. cheap. portable. theoretical grounding. rigor.

### 2014-07-21 Methods.tex
More commentary in methods

Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}). While there has been significant work on determining appropriate parameterisation for the model (e.g. \cite{Neilson2002}, \cite{Glockner2012}, \cite{Nilsson2011}), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.

@@

\begin{table}
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(n_{w}\) & Number of women & 1000 \\ \hline
\(n_{m}\) & Number of midwives & 100 \\ \hline
\(r_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(q_{w}\) & Probability of women sharing & 0. \\ \hline
\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(X_{h} - 1)\)} \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

>>>>

Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}). While there has been significant work on determining appropriate parameterisation for the model (e.g. \cite{Neilson2002,Glockner2012,Nilsson2011}, and particularly \citet{Byrnes1999,Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work. For simplicity, it is assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive \citep{Humphriss2013}. The scenario is biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty. Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.

@@

\begin{table}[h!]
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(n_{w}\) & Number of women & 1000 \\ \hline
\(n_{m}\) & Number of midwives & 100 \\ \hline
\(r_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(q_{w}\) & Probability of women sharing & 0. \\ \hline
\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(x_{h} - 1)\)} \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}
